### 2016-06-30 ch06-concl/conclusions.tex
IRF truncation + stability issues

>>>>

    \subsubsection{Impulse Response Truncation}
    With respect to the impulse response truncation approaches introduced in \secref{sec:nonparametric:truncation}, a few paths could be investigated further to broaden the class of systems where these methods are applicable and have a more subtle smoothing behavior of the transfer function.

    The crude truncation approach that is discussed in this thesis, can be interpreted as equivalent to windowing the \gls{IRF} with a rectangular window.
    In the frequency domain, this causes a very obvious correlation in the \gls{FRF}.
    By choosing a different window function (e.g. an exponential window, Hann window, \ldots), one could try to reduce this adverse effect.

   Another alternative for this crude rectangular windowing approach, which still uses a \gls{DFT} for the full size of the measurement record, could be to reduce the size of the \gls{DFT}.
   The introduced algorithms that determine a truncation length $\truncTime$, could also give a good indication of what size of \gls{DFT} would be suitable to represent the system well for the given measurements.
   However, further studies are required to compare the performance of these different alternatives.

   Currently, the truncation approach works based on the assumption that the last fragment of the \gls{IRF} is dominated by noise influences.
   The consequence of this is that the system is assumed to be stable and causal.
   It would be a worthwhile extension to relax this assumption to deal with unstable systems as well.
   For those systems, the last fragment of the \gls{IRF} will be dominated by the unstable (or anti-causal) part of the system. 
   Hence, the problem will become much harder to deal with, since a segment in the middle of the \gls{IRF} needs to be found where the noise level can be estimated.
   Afterwards, one could try to split up the \gls{IRF} in a part attributed to the stable poles and one caused by unstable poles and apply truncation on both parts separately and recombining the results.
